\chapter{\label{ch:req_and_specs} Requirements and Specifications}

This project builds on the primary objective of enhancing human-robot interaction (HRI) by integrating Augmented Reality (AR) into a mobile robot. As outlined in Section \ref{sec:objectives}, the system needs to meet specific requirements to ensure it performs as intended. These requirements were established through research, discussions with supervisor, and analysis of the intended user environment. The requirements are designed to guide both the technical implementation and the user experience, ensuring the robot operates seamlessly with AR-based control systems.

\begin{itemize}
    \item \textbf{R1.} The robot must operate in different control zones, defined by AR markers, and adjust its behavior accordingly (e.g., slowing down, stopping, or performing a task).
    \item \textbf{R2.} The system must integrate dynamic instructions based on ArUco marker detection, allowing for real-time task updates.
    \item \textbf{R3.} The robot must map its environment using visual markers and avoid obstacles based on AR feedback.
    \item \textbf{R4.} The AR interface must provide real-time visual feedback for the human operator to improve task monitoring and control.
    \item \textbf{R5.} The robot must include object avoidance functionality, ensuring it maintains a safe distance from recognized obstacles (e.g., warning cones) based on AR markers.
    \item \textbf{R6.} The system should detect and respond to wheel slip events caused by changes in surface traction, providing stability during operation.
\end{itemize}

To meet these requirements, the system will implement the following functionalities:

\begin{itemize}
    \item \textbf{F1.} Implementation of AR-based control zones that dynamically adjust robot speed, direction, or initiate tasks based on detected markers (R1).
    \item \textbf{F2.} Real-time processing of ArUco markers to update task instructions and provide context-specific navigation and task execution (R2).
    \item \textbf{F3.} The robot will use visual markers for environmental mapping and will avoid obstacles based on this feedback (R3).
    \item \textbf{F4.} AR-based visual feedback will provide the human operator with real-time monitoring of the robot’s actions and environmental interactions (R4).
    \item \textbf{F5.} Integration of object avoidance behavior, ensuring the robot maintains a safe distance from obstacles based on AR marker detection (R5).
    \item \textbf{F6.} Implementation of wheel slip detection functionality that monitors the robot's power draw to identify surface traction changes (R6).
\end{itemize}

Testing will be performed to ensure that the system meets the outlined requirements and functionalities. The table below shows the breakdown of the sub-tests to be performed, with each test linked to the specific functions and requirements it checks.

\begin{table}[ht]
\centering
\caption{Breakdown of sub-tests to be performed in the acceptance testing.}
\label{tab:testing}
\begin{tabular}{|c|p{5cm}|c|c|}
\hline
\textbf{Test Number} & \textbf{Description} & \textbf{Functions Checked} & \textbf{Requirements Tested} \\ \hline
T1                   & Test the robot’s behavior in AR-based control zones   & F1  & R1   \\ \hline
T2                   & Test real-time ArUco marker detection for dynamic instructions & F2  & R2   \\ \hline
T3                   & Test environmental mapping and obstacle avoidance based on AR markers & F3  & R3, R5 \\ \hline
T4                   & Test AR-based visual feedback for real-time monitoring & F4  & R4   \\ \hline
T5                   & Test object avoidance system using visual markers   & F5  & R5   \\ \hline
T6                   & Test wheel slip detection and response functionality & F6  & R6   \\ \hline
\end{tabular}
\end{table}


